Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-11-17 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Little comments

Like any other dataset, clustered datasets are prone to missing data. Several strategies can be used to handle missing data, including complete case analysis and imputation. We focus on the latter approach and discuss statistical methods for replacing the missing data with one or more plausible values. Afterwards, the completed data can be analyzed as if they were completely observed. In contrast to single imputation (where missing data are only replaced once), multiple imputation allows to preserve uncertainty due to missingness and is therefore recommended (c.f. Rubin 1976).

@@

To develop the best imputation model for the incomplete variable `popular`, we need to know whether the observed values of `popular` are related to observed values of other variables. Plot the pair-wise complete correlations in the incomplete data:

@@

>>>>

<!-- Maybe besides CC and imputation name also likelihood based methods -->
Like any other dataset, clustered datasets are prone to missing data. Several strategies can be used to handle missing data, including complete case analysis and imputation. We focus on the latter approach and discuss statistical methods for replacing the missing data with one or more plausible values. Afterwards, the completed data can be analyzed as if they were completely observed. In contrast to single imputation (where missing data are only replaced once), multiple imputation allows to preserve uncertainty due to missingness and is therefore recommended (c.f. Rubin 1976).

@@

To develop the best imputation model for the incomplete variable `popular`, we need to know whether the observed values of `popular` are related to observed values of other variables. Plot the pair-wise complete correlations in the incomplete data:
<!-- Excelent, but i dont know if you can refer to the outflux criteria here or elsewhere, cuz in practice it is used to select the predictors in the imputation model from dataset with a lot of features-->

@@

<!-- A fixed cluster model is better if we have data with all the clusters in the population and we are interested in knowing the effect of a treatment on the specific cluster eg. Cluster No.123. If the population is too large (10000 schools) and we have a sample (200 schools) then an random cluster is better and saves us degrees of freedom because some of the parameters are random variables. Here we have to say that the imputation model should be more in line with the analysis model (that defines in part how the cluster is included) and consider how the estimation of the imputation model could be affected when N is too large (as we add N dummies in the fixed cluster model) or if ni is too small in some clusters, so the model can not be estimated in them.. -->
